---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# yg

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

[![CRAN status](https://www.r-pkg.org/badges/version/yg)](https://cran.r-project.org/package=yg)

The yg r package read yeast grower ini-formatted text files.

## Installation

<!-- You can install the released version of yg from [CRAN](https://CRAN.R-project.org) with: -->

``` r
install.packages("yg") # not yet.
remotes::install_github("npjc/yg")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(yg)
path <- yg_example('05_09_13_RT1-79_ps1_A_96_T_13.txt')
d <- read_yg(path)
```

returns a nested tibble, with info and data sections.

**N.B. yg file names are prefixed with `dd_mm_yy_` and `read_yg()` uses this information to compute the `datetime` variable in the data field**

```{r structure}
str(d, 1)
```

data variable has the measurement / growth data:

```{r data}
d$data[[1]]
```

info variable has other info:

```{r info}
dplyr::glimpse(d$info[[1]])
```

