---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/readyg)](https://cran.r-project.org/package=readyg)

Read, Validate, Simulate and Write YeastGrower (aka ACCESS) files.

## Installation

<!-- You can install the released version of yg from [CRAN](https://CRAN.R-project.org) with: -->

``` r
# install.packages("readyg") # not yet.
remotes::install_github("npjc/readyg")
```

## Example

Yeast Grower/ACCESS files are written in windows ini format (*sort-of*). `read_yg()` parses this format and returns the data in a format suitable for analysis or exporting (writing) to a `.csv` files.

```{r example}
library(readyg)
files <- yg_example_files()
files[1] # one example file
d <- read_yg(files[1])
d
```

In the individual sections:

```{r sections}
d$data
d$run_params
d$drug_data
```

If you want the information in the other sections , you can use `read_ini()` 
instead. This parses the ini file into a list:

```{r as-ini}
l <- read_ini(files[1])
str(l, 1)
```

## Additional Info

YeastGrower/ACCESS encodes data in non-standard ways that `read_yg()` corrects:

**data section:**

* the temperature field may be written as `300`, `30`, `30.0` to indicate 30ºC.  
* the datetime field in the data may be written as ` D0_12:11:10`, `D0 _12:11:10` or `12:11:10` to indicate 12:11:10 on the first day of the run. To indicate what date `D0` is you can provide this as an argument to e.g. `read_yg('path/to/file.txt', start_date = 'YYYY-MM-DD')`.  
    * N.B. if the datetime field is encoded as `12:11:10` and the run last longer that one day the current results may be erroneous. e.g. `12:11:10, ... , 23:48:17, ... , 00:12:34` would be encoded as the same day. This is the safe default but will provide an option to 'fix' this in the future.  
* well field: The well field is encoded in row-major order ('standard') for 6,24,96, and 384 well plates but ACCESS uses a custom ordering for 48 well plates. Currently, we remap these to the standard arangement so that the wells names of a 48-well plate follow the standard convention.  
    * N.B. the drug_data section, if present, can contain a `Well_Alias` field which is currently not checked for this inconsistency. Handle with care if using this information.  

**all the keys**

The Yeast Grower format has some use of nearly 3000 separte keys (fields). To retrieve all of them:

```{r keys-by-section}
yg_section_keys()
```

